True versus apparent shapes of astrophysical bow shocks

### 2017-04-03 papers/Paper1/quadrics-appendix.tex
Discussion of extinction to bow shock sources
Write more on interpretation of p-values

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/p-value-histogram}
  \caption{Histogram of \(p\)-values for all Anderson--Darling
    non-parametric 2-sample tests performed during the analysis of
    section~\ref{sec:comp-with-observ}.  The vertical dashed line
    shows the traditional threshold value for significance:
    \(p = 0.05\). The red solid line shows the expected distribution
    of \(p\)-values that would be obtained if no significant
    correlations existed.}
  \label{fig:histo-p-values}
\end{figure}

@@

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/p-value-histogram}
  \caption{Histogram of \(p\)-values for all Anderson--Darling
    non-parametric 2-sample tests performed during the analysis of
    section~\ref{sec:comp-with-observ}.  The vertical dashed lines
    shows the traditional threshold values for significance:
    \(p = 0.001\) and \(p = 0.05\). The red solid line shows the
    expected uniform distribution of \(p\)-values that would be
    expected if the null hypothesis were always true, that is, if no
    significant correlations existed.}
  \label{fig:histo-p-values}
\end{figure}

The \(p\)-values are the probability of finding a difference between
two populations as large as (or larger than) what is observed,
\emph{given} that there is no difference in the underlying
distribution from which the two populations are drawn (that is, given
that the null hypothesis is true).  However, what we really want to
know is something else: the probability that the null hypothesis is
true, \emph{given} the observations.  That is, the probability,
\(\alpha\), of a \textit{false positive}, also known as the \textit{Type I
  error rate}.  The common mistake of conflating these two definitions
is known as the ``\(p\)-value fallacy'' \citep{Goodman:1999a}, or``the
error of the transposed conditional'', as discussed in detail by
\citet{Colquhoun:2014a}.  It is possible to derive \(\alpha\) from
\(p\) using Bayes' theorem (e.g., \citealp{Goodman:1999b}), but that
requires an estimate of the prior probability of the null hypothesis,
independent of the observations.  Alternatively, it is also possible to find a lower bound on \(\alpha\) from a frequentist approach \citep{Sellke:2001a}:
\begin{equation}
  \label{eq:type-I}
  \alpha(p) \ge \bigg[ 1 - \big(e p \ln p\big)^{-1} \bigg]^{-1}
\end{equation}

\begin{table}
  \caption{Lower bounds on the Type~I error rate, \(\alpha\)}
  \label{tab:type-I}
  \centering
  \begin{tabular}{lrr} \toprule
    Correlation & \(p\) & \(\alpha\) \\
    \midrule
    \multicolumn{3}{l}{\itshape Quantitative \dotfill}\\
    \(R_c\) vs \(R_0\) & \textit{0.0054} & \textit{0.0712} \\
    \(R_{90}\) vs \(R_0\) & \textbf{0.0001} & \textbf{0.0025} \\
    \(R_c\) vs \(H_0\) & 0.1229 & 0.4119 \\
    \(R_{90}\) vs \(H_0\) & \textit{0.0215} & \textit{0.1833} \\
    \(R_c\) vs \(A_K\) & 0.19 & 0.4617 \\
    \(R_{90}\) vs \(A_K\) & 0.63 & 1 \\
    \(R_c\) vs \(|b|\) & 0.19 & 0.4617 \\
    \(R_{90}\) vs \(|b|\) & 0.31 & 0.4967 \\
    \(R_c\) vs \(\cos(\ell)\) & 1.00 & 1 \\
    \(R_{90}\) vs \(\cos(\ell)\) & 0.36 & 0.4999 \\
    \midrule
    \multicolumn{3}{l}{\itshape Categorical} \dotfill\\
    \(R_c\) vs Facing & 0.71 & 1 \\
    \(R_c\) vs H II & 0.50 & 1 \\
    \(R_{90}\) vs Facing & 0.60 & 1 \\
    \(R_{90}\) vs H II & 0.52 & 1 \\
    \(R_c\) vs Multiple & 1.00 & 1 \\
    \(R_{90}\) vs Multiple & 0.34 & 0.4993 \\
    \(R_c\) vs \SI{8}{\um} & 0.82 & 1 \\
    \(R_{90}\) vs \SI{8}{\um} & 0.6 & 1 \\
    \midrule
    \multicolumn{3}{l}{\itshape Other datasets} \dotfill\\
    \(R_c\) vs Herschel & 0.074 & 0.3437 \\
    \(R_{90}\) vs Herschel & \textbf{0.00052} & \textbf{0.0106} \\
    \(R_c\) vs M42 & \textbf{0.00048} & \textbf{0.0099} \\
    \(R_{90}\) vs M42 & \textbf{0.0000105} & \textbf{0.0003} \\
    \bottomrule
  \end{tabular}
\end{table}

@@

The p-curve \citep{Head:2015a}

### 2017-04-03 papers/Paper1/sec-quadrics-observations.tex
Write more on interpretation of p-values

We now investigate if the bow shock shapes of the MIPSGAL sources are
correlated with any other parameters via the following methodology:
\begin{enumerate}[1.]
\item For each of the parameters in the \citet{Kobulnicky:2016a}
  catalog, we divide the sources into two or more sub-samples,
  according to the value of the parameter.  For quantitative
  parameters, such as those discussed in the previous section, we use
  two sub-samples of equal size, with membership determined by whether
  the parameter is larger or smaller than the median value.  But we
  also use categorical parameters, such as the type of bow shock
  environment, or the presence/absence of \SI{8}{\um} emission, in
  which case the sub-samples are of unequal size.
\item We plot the KDEs of the two sub-samples separately on the
  \(R_c\)--\(R_{90}\) plane (see Figs.~\ref{fig:mipsgal-correlated} and
  \ref{fig:mipsgal-uncorrelated}) to check for any obvious
  differences.
\item We test if there is any statistically significant difference
  between the shape distributions of the sub-samples by applying the
  2-sample Anderson--Darling test \citep{Anderson:1952a, Scholz:1987a} to the
  \(R_c/R_0\) and \(R_{90}/R_0\) distributions separately.  This is a
  non-parametric test of the \textit{null hypothesis} that the two
  sub-samples are drawn from the same distribution.

\end{enumerate}

>>>>

We now investigate if the bow shock shapes of the MIPSGAL sources are
correlated with any other parameters via the following methodology:
\begin{enumerate}[1.]
\item For each of the parameters in the \citet{Kobulnicky:2016a}
  catalog, we divide the sources into two or more sub-samples,
  according to the value of the parameter.  For quantitative
  parameters, such as those discussed in the previous section, we use
  two sub-samples of equal size, with membership determined by whether
  the parameter is larger or smaller than the median value.  But we
  also use categorical parameters, such as the type of bow shock
  environment, or the presence/absence of \SI{8}{\um} emission, in
  which case the sub-samples are of unequal size.
\item We plot the KDEs of the two sub-samples separately on the
  \(R_c\)--\(R_{90}\) plane (see Figs.~\ref{fig:mipsgal-correlated} and
  \ref{fig:mipsgal-uncorrelated}) to check for any obvious
  differences.
\item We test if there is any statistically significant difference
  between the bow shock shapes of the sub-samples by applying the
  2-sample Anderson--Darling test \citep{Anderson:1952a, Scholz:1987a}
  to \(R_c/R_0\) and \(R_{90}/R_0\) separately.  This is a
  non-parametric test of the \textit{null hypothesis} that the two
  sub-samples are drawn from the same distribution.  It returns a
  \(p\)-value, which is the estimated probability that the observed
  difference between the two sub-samples would be as large as it is
  purely by chance if they were all were drawn from the same
  distribution.  We adopt a threshold of \(p < 0.001\) in order to
  confidently reject the null hypothesis and declare a ``significant''
  difference between the two sub-samples, but we also consider the
  less strict threshold of \(p < 0.05\) as an indicator of
  ``probable'' difference (see Appendix~\ref{sec:distr-p-values} for
  details).
\end{enumerate}
